Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-28 providence/sections/intro.tex
small changes

\npara{\bf Full Hand Count:} It is worth noting here that if election officials do not have a plan for when they will move to a full hand count, and the election outcome is incorrect, at least a fraction $(1-\alpha)$ of the audits will {\em never} stop, and new rounds will continue to be drawn. See Figure \ref{fig:prov-risk} in section \ref{sec:sims} for the results of 10,000 simulations of \Providence on tied elections (risk limit of 0.1, across election margins of 0.05 and larger in the statewide contests for US President in 2020). Observe that, for each margin studied, more than 90\% of the audits do not stop after five rounds. To illustrate this idea, we present two example simulations from among those used to compute the statistics reported in Figure \ref{fig:prov-risk}.

@@

The first simulation assumed that the tally is correct and resulted in 1,138 votes for Trump and 1,054 for Biden (the rest were irrelevant votes) and the audit stopped because: \[ \omega ^{-1} = 0.047 < \alpha \]

>>>>

\npara{\bf Full Hand Count:} It is worth noting here that if election officials do not have a plan for when they will move to a full hand count, and the election outcome is incorrect, at least a fraction $(1-\alpha)$ of the audits will {\em never} stop, and new rounds will continue to be drawn. See Figure \ref{fig:prov-risk} in section \ref{sec:sims} for the results of 10,000 simulations of \Providence on tied elections (risk limit of 0.1, across election margins of 0.05 and larger in the statewide contests for US President in 2020). Observe that, for each margin studied, more than 90\% of the audits do not stop after five rounds. To illustrate this idea, we present two example simulations from among those used to compute the statistics reported in section \ref{sec:sims}.

@@

The first simulation assumed that the tally is correct and resulted in 1,138 votes for Trump and 1,054 for Biden (the rest were irrelevant votes). The audit stopped because: \[ \omega ^{-1} = 0.047 < \alpha \]

### 2023-02-28 providence/sections/model.tex
small changes

The ratios for \BRAVO and \Minerva are for two candidates. As mentioned when describing the example in section \ref{sec:intro-model}, audits of multiple-candidate contests are treated as multiple audits of the pairwise contest between the announced winner and all other candidates.

>>>>

The ratios for \BRAVO and \Minerva are for two candidates. As mentioned when describing the example in section \ref{sec:intro-model}, audits of multiple-candidate contests are treated as multiple audits of the pairwise contests between the announced winner and all other candidates.

### 2023-02-28 providence/sections/prov.tex
small changes

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, expressions relating the risks are not available, and we are not able to obtain an expression bounding the sum of the risks across rounds. Thus we are not able to determine if \Minerva is an RLA in this case, or if it is vulnerable to the strongly round-choosing adversary \cite{usenix_minerva, arxiv_athena, alpha}.

@@

Notice that \Providence requires the computation of $\tau_j$ for $j=1$ and no other values of $j$. The value of $\tau_1$ is simply the ratio of the the tails of the binomial distributions (the distributions are binomial because the auditing is with replacement) for the two hypotheses and can be fairly efficiently computed. The computation of $\tau_j$ for $j \geq 2$, as required in \Minerva, relies on the convolution of two probability distribution functions and is hence computationally considerably more expensive. Smaller computational complexity makes audit planning and analysis using simulations as in section~\ref{sec:workload} more feasible.

>>>>

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$ for which the audit stops, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, expressions relating the risks are not available, and we are not able to obtain an expression bounding the sum of the risks across rounds. Thus we are not able to determine if \Minerva is an RLA in this case, or if it is vulnerable to the strongly round-choosing adversary \cite{usenix_minerva, arxiv_athena, alpha}.

@@

Notice that \Providence requires the computation of $\tau_j$ for $j=1$ and no other values of $j$. The value of $\tau_1$ is simply the ratio of the the tails of the binomial distributions (the distributions are binomial because the sampling is with replacement) for the two hypotheses and can be fairly efficiently computed. The computation of $\tau_j$ for $j \geq 2$, as required in \Minerva, relies on the convolution of two probability distribution functions and is hence computationally considerably more expensive. Smaller computational complexity makes audit planning and analysis using simulations as in section~\ref{sec:workload} more feasible.
